### 2013-10-14 article.tex
Grammar.

% INTRODUCTION
\section*{Introduction} % The \section*{} command stops section numbering
\addcontentsline{toc}{section}{\hspace*{-\tocsep}Introduction} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
\label{sec:introduction}
% Background and Challenge
%	Vilket sammanhang utgör studiens bakgrund?
%	Vilka utmaningar omfattar studien?
When developing \textit{GPGPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
between on-chip hardware. Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-
technologies.\\
\\
% Approach and Result
%	Vilken ansats tillämpas i studien?
%	Vilka resultat gav studien?
The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from graphics cards - possibly due to architectural differences in-between chip manufacturers. A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for a substantial performance-loss. This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
This study concerns an investigation into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some precision. \\
A logical next step of such an evaluation would be to investigate any influence Microsoft WARP may have on computational precision. Thus, it is important that the result such a kernel would produce is measurable and deterministic. \\
\\
This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity. As such, Microsoft \textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft. Link to Microsofts page on WARP here!}.\\
\\
% Outline and Conclusion
%	Vilket upplägg har resterande delar av matrialet?
As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.

>>>>

% INTRODUCTION
\section*{Introduction} % The \section*{} command stops section numbering
\addcontentsline{toc}{section}{\hspace*{-\tocsep}Introduction} % Adds this section to the table of contents with negative horizontal space equal to the indent for the numbered sections
\label{sec:introduction}
% Background and Challenge
%	Vilket sammanhang utgör studiens bakgrund?
%	Vilka utmaningar omfattar studien?
When developing \textit{GPU}-kernels relatively small changes may induce large deviations in performance, due to massively parallelized instruction sets and architectural differences in-
between on-chip hardware. Therefore, it may be desirable for the developer to be able to view the data he or she is modifying on the graphics card - a possibility often limited in terms of \textit{GPGPU}-
technologies.\\
\\
% Approach and Result
%	Vilken ansats tillämpas i studien?
%	Vilka resultat gav studien?
The increased utilization of \textit{GPGPU} has brought forth the need of more extensive debugging-possibilities involving access of data that may be hard to retrieve from graphics cards - possibly due to architectural differences in-between chip manufacturers. A preferred solution to this problem has been to emulate such \textit{GPU}-kernels on the \textit{CPU} - in exchange for a substantial performance-loss. This study comprises an investigation into the performance of software emulation of hardware accelerated \textit{GPU}-kernels, by the means of analyzing several software rasterizers.\\
Furthermore, this study concerns inquiry into the DirectCompute-framework on the Windows-platform, analyzing the performance of a \textit{GPGPU}-kernel on-chip, using the DirectX standard software rasterizer, and utilizing the DirectX 11.1-addition\footnote{Bundled with Windows 8.} Microsoft \textit{WARP}-technology (Windows Advanced Rasterization Platform) - which promises high-speed software emulation in exchange for some computational precision. \\
A logical next step of such an evaluation would be to investigate any influence Microsoft WARP may have on computational precision. Thus, it is important that the result such a kernel would produce is measurable and deterministic. \\
\\
This study concludes that the performance loss of emulated \textit{GPGPU}-kernel may be considered negligible in exchange for possible extended possibilities of data extraction and increased granularity. As such, Microsoft \textit{WARP}-technology may be considered feasible for use in industry rasterization\footnote{Such a use-case might be if hardware is unavailable, not suffiecient or busy - as suggested by Microsoft. Link to Microsofts page on WARP here!}.\\
\\
% Outline and Conclusion
%	Vilket upplägg har resterande delar av matrialet?
As such, the study concerns the fields of simulation, emulation and \textit{GPU}-technologies - respectively, with the purpose of facilitating debugging and profiling of \textit{GPU}-kernels, whilst maintaining acceptable performance.
